Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
Go back to the old definition of states (which somehow got lost)

A programs $P$ is represented as a transition systems with state space $X$,
transition relation $T \subseteq X \times X$, and set of variables $V$.  A
state of the program is a valuation of the variables from $V$.  For a state
$x \in X$ with $T(x,x')$ we say $x'$ is the successor of $x$ under $T$.

@@

>>>>

A programs $P$ is represented as a transition system with state space $X$ and
transition relation $T \subseteq X \times X$.  For a state
$x \in X$ with $T(x,x')$ we say $x'$ is a successor of $x$ under $T$.
If each state $x$ has at most one successor $x'$, then we say that $T$ is
deterministic.

@@

Key: \tick = terminating, \xmark = non-terminating.
